### 2016-07-26 notions.tex
comments about privacy

In addition to correctness, we establish notions of privacy for set-representations.  We explore two notions.  The first has the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\aux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\aux,q)$ on queries~$q$ of its choosing.  At the end of this game, the adversary must output some point in the set represented by~$M$.  In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size), and is given $(M,\aux)$ where~$M$ represents $S_b$ for a uniform bit~$b$.  In this game, the adversary must determine which set~$M$ represents.

@@

\tsnote{Is this the right kind of indistinguishability anyway?  It seems to me that we want to say that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented.  One way to capture this would be indistinguishability with respect to the query set~$\calQ$: you are handed $(M,\aux)$ and you need to output a query~$q\in\calQ$ such that $q(S_0) \neq q(S_1)$.  But this doesn't really capture that $(M,\aux)$ on their \emph{own} do not leak information about the set.  (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)  I don't know, this is tricky... How do you handle the fact that, under our current syntax, $M$~may contain secrets, e.g. a PRP key?}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

>>>>

In addition to correctness, we establish notions of privacy for set-representations.  We explore two notions.  The first has the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\aux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\aux,q)$ on queries~$q$ of its choosing.  At the end of this game, the adversary must output some point in the set represented by~$M$.  In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two. Then the adversary is given $\aux$ and oracle access to $\Qry(M,\aux,q)$, and it must decide which set~$M$ represents.

@@

\tsnote{Is this the right kind of indistinguishability anyway?  This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\aux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented, period?  (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   I don't know, this is tricky... Also, if you give~$M$ to the adversary, how do you handle the fact that, under our current syntax, $M$~may contain secret keys, etc.?}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}
